---
title: "penguin_assignment"
output: html_document
date: "2022-12-06"
---

## This rmd provides code to load palmerpenguin data, clean it, runs a statistical test on the data, plots the figure from this test and saves the figure as a png file and a svg file. 
## Set working directory 
```{r}
setwd("/Users/R/penguinproject")
```


## Load the libraries from my files 
```{r}
source("functions/libraries.r")
```

# Load the functions from my files 
```{r}
source("functions/cleaning.r")
source("functions/plotting.r")
```

# Load the data
```{r}
penguins_raw <- read.csv("data_raw/penguins_raw.csv")
```


# Clean the data 

## Fix the column names, remove empty rows, remove columns called comment and delta 
```{r}
penguins_clean <- cleaning(penguins_raw)

```
## Save the clean data
```{r}
write.csv(penguins_clean, "data_clean/penguins_clean.csv")
```


## Use the function to remove rows that have NA for either flipper or mass data and remove everything excepts species, body mass and flipper length data. 
```{r}
penguins_mass_and_flippers <- remove_empty_flipper_and_mass(penguins_clean)
head(penguins_mass_and_flippers)
```


# Statistical Test - Linear regression 
### Null hypothesis: flipper length cannot be predicted from body mass in penguins 

```{r results='hide'}
penguin_mod1 <- lm(flipper_length_mm ~ body_mass_g, penguins_mass_and_flippers)

summary(penguin_mod1)
```

### ANOVA test on the linear regression 
```{r}
anova(penguin_mod1)
```
#### The P value is below 0.05 this means we can reject the null hypothesis and therefore can conclude that body mass can be used to predict flipper length in penguins. 


##Plotting the model 
```{r}
scattergraph_penguins <- plot_penguin_figure(penguins_mass_and_flippers)
scattergraph_penguins
```



# Save figures
##save the figure as a svg file
```{r}
save_scattergraph_svg(penguins_mass_and_flippers, 
                      "figures/fig01_vector.svg", 
                      size = 15, scaling = 1)
```



##Save the figure for a report 
```{r}
save_scattergraph_png(penguins_mass_and_flippers, 
                      "figures/fig01_report.png", 
                      size = 15, res = 600, scaling=1)
```

##Save the figure for a presentation
```{r}
save_scattergraph_png(penguins_mass_and_flippers, 
                      "figures/fig01_powerpoint.png", 
                      size = 15, res = 600, scaling=1.4)
```

##Save the figure for a poster 
```{r}
save_scattergraph_png(penguins_mass_and_flippers, 
                      "figures/fig01_poster.png", 
                      size = 30, res = 600, scaling=2.8)
```





